Kung Faux Pandas \\ \large Simplifying privacy protection

### 2018-07-26 paper/amia.tex
Auto Update from local Sharelatex

\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
% \PassOptionsToPackage{numbers, compress}{natbib}
% before loading nips_2018

% ready for submission
%\usepackage{nips_2018}

% to compile a preprint version, e.g., for submission to arXiv, add
% add the [preprint] option:
\usepackage[preprint]{nips_2018}

% to compile a camera-ready version, add the [final] option, e.g.:
%\usepackage[final]{nips_2018}

% to avoid loading the natbib package, add option nonatbib:
% \usepackage[nonatbib]{nips_2018}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage[super]{nth}     % JK: for 1st-ing and 2nd-ing

\usepackage{graphicx}       % added by seth - image support
\graphicspath{ {./images/} }

@@

\urlstyle{same}
\title{%
  Kung Faux Pandas \\
  \large Simplifying privacy protection
  }

\author{
  James King, Seth Russell, Tellen D. Bennett, Debashis Ghosh\\
  Data Science to Patient Value (D2V)\\
  School of Medicine\\
  University of Colorado Anschutz Medical Campus\\
  Aurora, CO\\
  \texttt{\{james.king, seth.russell, tell.bennett, debashis.ghosh\}@ucdenver.edu}
  }

\date{May 2018}

@@

@@

\begin{abstract}
There are many barriers to data access and data sharing, especially in the domain of machine learning on health care data. Legal constraints, such as HIPAA, protect patient privacy but slow access to data and limit reproducibility. We provide a description of an end-to-end system called \emph{Kung Faux Pandas} for easily generating de-identified or synthetic data which is statistically similar to real data but lacks sensitive information. This system focuses on data synthesis and de-identification narrowed to a specific research question to allow for self-service data access without the complexities required to generate an entire population of data that is not needed for a given research project. Kung Faux Pandas is an open source publicly available\footnote{\url{https://github.com/CUD2V/kungfauxpandas}} system that lowers barriers to HIPAA- and GDPR-compliant data sharing for enabling reproducibility and other purposes.
\end{abstract}

@@

\bibliographystyle{unsrt}

>>>>

\documentclass{amia}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography
\usepackage[super]{nth}     % JK: for 1st-ing and 2nd-ing
\usepackage{graphicx}       % added by seth - image support
\graphicspath{ {./images/} }

@@

\urlstyle{same}

@@

\title{%
  Kung Faux Pandas \\
  \large Simplifying privacy protection
  }

\author{
  James King MIDS$^{1}$, Seth Russell MS$^{1}$, Tellen D. Bennett$^{1,2}$, MD, MS, Debashis Ghosh, PhD$^{1,3}$
  }

\institutes{
  $^1$CU Data Science to Patient Value (D2V), Anschutz Medical Campus, Aurora, CO;
  $^2$Pediatric Critical Care, University of Colorado School of Medicine, Aurora, CO;
  $^3$Biostatistics and Informatics, Colorado School of Public Health, Aurora, CO\\
}

@@

\noindent{\bf Abstract}

\textit{There are many barriers to data access and data sharing, especially in the domain of machine learning on health care data. Legal constraints, such as HIPAA, protect patient privacy but slow access to data and limit reproducibility. We provide a description of an end-to-end system called \emph{Kung Faux Pandas} for easily generating de-identified or synthetic data which is statistically similar to real data but lacks sensitive information. This system focuses on data synthesis and de-identification narrowed to a specific research question to allow for self-service data access without the complexities required to generate an entire population of data that is not needed for a given research project. Kung Faux Pandas is an open source publicly available\footnote{\url{https://github.com/CUD2V/kungfauxpandas}} system that lowers barriers to HIPAA- and GDPR-compliant data sharing for enabling reproducibility and other purposes.}

@@

\bibliographystyle{vancouver}
